Toward \earlywarning\ detection of gravitational waves from compact binary coalescence

### 2012-01-06 article.tex
Added clarification requested by Chad
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1446 ccdd05d5-56c1-461a-bf98-85f6876523b4
Added another clarification to section 5.5
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1448 ccdd05d5-56c1-461a-bf98-85f6876523b4

Modern (ca. 2011) workstations can achieve peak
computation rates up to $\sim$$10^{11}$~\flops.  In practice, we expect that a
software implementation of \lloid\ will reach average computation rates that are
perhaps a factor 10 less than this, $\sim$$10^{10}$~\flops\ per machine, due to
non-floating point tasks including bookkeeping and thread synchronization.
Given these considerations, we estimate that a full single-detector Advanced
\LIGO\ search with \lloid\ will require $\sim$$10$ machines.

@@

The overlap-save \FD\ method is slightly more efficient than LLOID for this particular sub-bank, requiring $5.2 \times 10^8$~\flops.  The scaling argument projects that a full \FD\ search would require $7.8 \times 10^{10}$~\flops.  The direct calculation from expression~(\ref{eq:fd-flops}) gives $5.9 \times 10^{10}$~\flops, in order-of-magnitude agreement.  It appears that in this application the conventional \FD\ search is scarcely a factor of 2 more computationally efficient than LLOID, but only at the price of thousands of seconds of latency.

>>>>

Modern (ca. 2011) workstations can achieve peak
computation rates up to $\sim$$10^{11}$~\flops.  In practice, we expect that a
software implementation of \lloid\ will reach average computation rates that are
perhaps a factor 10 less than this, $\sim$$10^{10}$~\flops\ per machine, due to
non-floating point tasks including bookkeeping and thread synchronization.
Given these considerations, we estimate that a full Advanced
\LIGO, single-detector, \NS--\NS\ search with \lloid\ in will require $\sim$$10$ machines.

@@

The overlap-save \FD\ method is slightly more efficient than LLOID for this particular sub-bank, requiring $5.2 \times 10^8$~\flops.  The scaling argument projects that a full \FD\ search would require $7.8 \times 10^{10}$~\flops.  The direct calculation from expression~(\ref{eq:fd-flops}) gives $5.9 \times 10^{10}$~\flops, in order-of-magnitude agreement.  In this application, the conventional \FD\ search is scarcely a factor of 2 faster than LLOID while gaining only $0.3$\% in \SNR, but only at the price of thousands of seconds of latency.
